Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-21 doc/PRF2022/PRF_main.tex
almost done results

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)-(b) show the average strain increase for bilayer, vesicle BL,
  multilamellar, and striated JP structures under a shear flow and a TG flow, respectively.
Panel (c)-(d) show the average alignment of four JP structures under a shear flow and a TG flow, respectively. 
Each snapshot of panels (e)-(l) contains the configurations of the JP structure using a specific type of boundary bondition without ruptures and the backgroud curves indicate the velocity streamlines.}
\end{figure}
%
We subjected the Type I, II, and III JP phases to background flows and measured 
their material response.  The background flows were a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
and vertical directions, respectively.
The shear flow replicates the motion of a fluid between two parallel,
moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the
$2\pi \lambda \times 2\pi \lambda$ TG cells.
Throughout, we use $\lambda = 2$ nm
so that the JP phases occupy about nine cells.

In both cases, $\dot \gamma$ is the shear rate.
The flow rate $\lambda \dot \gamma$  
was chosen so that \eqref{eq:tg_flow} has the same
rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
In other words, 
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
is the same for 
$\uu = \uu_{\infty}^{\text{sh}}$ as for 
$\uu = \uu_{\infty}^{\text{TG}}$
when integrated over a TG cell $A$.

To obtain a range for $\dot \gamma$, 
consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$ nm and $\kappa = 20\;\kbt$ are 
the characteristic phase sample radius 
and bending rigidity, respectively. 
That is, $\kappa$ gives the elastic stress 
for restoring the phase-sample shape.
Shear stress overcomes elastic stress   
when $C_a > 1$ and this yields 
$\dot \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$ s.
Thus our values for $\dot \gamma$ range between 
$0$ ns$^{-1}$ corresponding to quiescent flow
up to $0.2$ ns$^{-1}$ capable of rupturing the sample. 
Such shear rates are compatible with molecular dynamics 
simulation \cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels
\cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.

For initial data, the steady-state Type I amphiphiles phase
consisted of a number of disjoint bilayer components
(Figure \ref{fig:relax}(b)). To also have a single-component Type I phase, 
we reinitialized the data to have a ring-shaped vesicle bilayer.
This phase is distinguished from ``bilayer'' by ``vesicle BL'' in the figures.
For the same number of JP, the vesicle bilayer
has lower free  steady-state energy
($F = 24.6 \;\kbt$ nm$^{-1}$) than the 
disordered bilayer phase ($F = 27.2 \;\kbt$ nm$^{-1}$). 
Since the simulations are for two dimensions,
multiplying $F$ by a length gives the energy 
of a transversely invariant, three-dimensional 
phase.

Figure \ref{fig:s2esummary} (e)--(l) show the typical streamlines
for JP phases in background flow.  Although the plots only show
the region near the JP phases, the fluid velocity $\uu$ and 
order parameter $u$ are accounted for in all of $\mathbb{R}^2$.
Moreover, $\uu$ satisfies the rigid boundary condition at 
every JP-fluid interface i.e., the particles interact with the local
flow field and are not merely carried by background flow.

The simulation setup consisted of placing each of the 
phases in either a shear or TG background flow and then solving for the 
particle trajectories in time. In each setup, we solved for $500$ time steps 
with $\Delta t = 2$ ns, yielding time courses for $t \in [0, T]$, $T = 1$ $\upmu$s.
We then post-processed the trajectories.

Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}
contain the fully-resolved time courses for free energy $F$,
alignment order $S_2$, and strain $E$. The eight setups
correspond to the four JP phases---bilayer, vesicle BL, multilamellar,
and striated---and two background flows---shear and TG,
and the data are plotted with the same ordinate to facilitate
comparisons between simulation setups.  Each setup considers
a range of shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.

The fully-resolved time courses
in Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}
contain significant oscillations due to the particle-based formulation
and tumbling inherent to the background flows.  To extract meaningful
data, we further postprocessed the $F$, $S_2$, $E$ curves by taking
their time average over the interval $t \in [0, T]$.

\subsection{Strain and alignment}
\label{sec:strain-alignment}
The plots reveal highly distinct material responses from each phase.
Figure \ref{fig:s2esummary} (a) and (b) show the time-averaged
strain $\frac{1}{T}\int_0^T E \,\dif t$ over a broad
range of shear rates.  Strain $E$
measures the non-rigid-body deformation relative to the initial state
and expectedly increases with shear rate.
The greatest increase occurs with the Type I amphiphiles, 
suggesting that this phase has the lowest elastic modulus
(squares). In comparison, 
the  striated phase consisting of  Type III polar JP is
basically rigid (triangles).

Figure \ref{fig:s2esummary} (c) and (d) plot the time-averaged
alignment order $S_2$. The vesicle and striated phases possess
the greatest alignment order and, 
for the most part, $S_2$ decreases with increases in shear rate.
But there is an exception.  The Type I bilayer phase alignment
order actually increases under both shear and TG flows (solid squares).  
This suggests that 
the mixing action of background flow has the effect of moving the
disordered bilayer phase out of a local equilibrium and into a state
with greater order.
This surprising increase, 
brought about by combining previously broken bilayer 
end caps, is accompanied
by a slight decrease in free energy (Figure \ref{fig:fsummary}a, solid squares).

The sudden jumps in  Figure \ref{fig:s2esummary} (a) and (b)
and commensurate drops in panels (c) and (d) indicate
the existence of a critical shear rate $\gamma_*$.  This means that 
for $\gamma < \gamma_*$, the JP phase remains intact while
for $\gamma > \gamma_*$, the phase ruptures. 
For example, the vesicle BL phase has 
$\gamma_*$ approximately $0.05$ ns$^{-1}$ 
under shear flow and TG flow. However, the critical shear rate
is flow-pattern dependent because 
the striated phase has $\gamma_* = 0.14$ ns$^{-1}$ under shear flow
while $\gamma_* = 0.05$ ns$^{-1}$ under  TG flow.
Due to variable stress distribution, 
the critical shear rate in TG flow likely 
depends on the cell size parameter $\lambda$.
The disordered bilayer phase does not really possess a critical
shear rate because it already consists of several, disjoint components.
The jump in Figure \ref{fig:s2esummary} (a) (solid squares)
simply corresponds to disjoint components drifting apart in the shear
flow.  The Type II multilamellar phase did
not rupture for any of the shear rates considered.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{FSummary.pdf}
\end{center}
\caption{\label{fig:fsummary}
  The change of average free energy versus shear rates for shear flow and TG flow simulation results are plotted in panels (a)-(b). Panel (c) contains quadratic fits
  to the change in free energy as a function of displacement in interparticle distance
  from equilbrium.}
\end{figure}

\subsection{Free energy}
\label{sec:free-energy}
Figure \ref{fig:fsummary} plots the time-averaged
relative free energy $\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$ is 
\eqref{eq:free_energy2} at $t = 0$.  The 
greatest increase occurs with the Type II 
multilamellar phase, with the other phases 
showing a moderate change in a few \KBT\,nm$^{-1}$.

Figure \ref{fig:fsummary} (c) plots free energy 
against the displacement $x = c E$ representing the
change in mean  interparticle displacement from equilibrium;
$c = 1.25$ nm is particle radius.
The energies in Figure \ref{fig:fsummary} (c) are essentially  
quadratic in $x$ suggesting that the interactions 
are harmonic locally around equilibrium.
The harmonic bond strength is strongest between 
polar JP, and greater by a factor of two and five than
that for asymmetric hydrophobes and amphiphiles,
respectively.  This makes sense when considering 
that the free energy of the steady-state striated
phase is also greatest (Figure \ref{fig:relax} (c), around 85 \KBT\;nm$^{-1}$).
However, the bond strength in the multilamellar 
phase comes in second, despite having least steady-state free energy
(around 15 \KBT\;nm$^{-1}$).
The data point to the fact that the binding properties 
do not merely scale with free energy, 
but also involve the details of the interface's
hydrophobicity 
which are tuned by \eqref{eq:bc-type} in our model.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{RheologySummary.pdf}
\end{center}
\caption{\label{fig:rheologysummary}
  Rheology of Type I, II, and III phases.
  Panel (a) shows that bilayer phases  behave as a Newtonian fluid.
  Panel (b) provides that the multilamellar phase shows a near shear thinning behaviour.
  A pseudoplastic behaviour of deformation in striated phases is shown in panel (c). }
\end{figure}

\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely
constant strains maintained by an external force provided by   
background flow. Now we consider dynamic material properties.
Specifically, we look at the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that 
the shear flow $\uu_{\infty}^{\text{sh}}$
simulations correspond to a complex fluid within a drag plate
rheometer where the shear stress is set by $\mu \dot\gamma$  
and the observed, sample shear rate is $\dot E$. 
The definitions carry over to the TG flow case directly. 
Also, as a practical consideration,
the rotation of non-isotropic JP phases in the background 
flow leads to oscillation in the strain time courses 
making systematic fitting challenging (see 
Supplementary Material Figures \ref{fig:ulshraw}--\ref{fig:sttgraw}). 
The integral in \eqref{eq:strainrate} averages out these oscillations
and gives physically meaningful values.

The shear stress--strain rate data are 
excellently fit by power laws.  
Figures \ref{fig:rheologysummary} (a), (b), and (c)
show the data for Type I, Type II and Type III JPs, respectively,
under both shear flow (squares) and TG flow (triangles).
The bilayer phases consisting of Type I JPs are basically Newtonian
with viscosity $0.014$ MPa\;$\upmu$s $= 14$ mPa\;s,
about 14 times the the viscosity of water at room temperature
(Figures \ref{fig:rheologysummary}(a), dashed curve). 
The vesicle bilayer phase is slightly shear thickening
(Figures \ref{fig:rheologysummary}(a), solid curve).
The multilamellar phase consisting of Type II JPs
is somewhat shear thinning,  but its viscosity 
is larger than for Type I.  Finally, the striated
phase is strongly shear-thinning.  This 
further explains the rigid-like behavior of the 
striated phase found in the strain, shear-rate relationships from 
Figure \ref{fig:s2esummary}(a), (b) (triangles).
\todo[inline]{RBC flow refereces}

@@

\subsection{Discussion}
We choose the range of shear rates $\dot \gamma \in [0, 0.02]$ ns$^{-1}$
by analyzing the capillary number of the JP phases.  With this range, 
there was a critical shear rate $\dot \gamma_*$ for the vesicle BL
and striated phases where shear stresses exceeded elastic stresses,
leading to rupture.  The multilamellar phase did not rupture.
By varying model parameters, we can perform a dimensional analysis 
on $\dot \gamma_*$. Focusing on Type III JPs in shear flow, 
$\dot \gamma_* = 0.14$ ns$^{-1}$ for the basic model parameters
(see Section \ref{sec:tunable_hydrophobicity}).  Increasing
and decreasing the tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
$\Delta \gamma/\gamma$) led to basically the same relative
increase/decrease in critical shear
rate (denoted $\Delta \dot \gamma_*/\dot \gamma_*$).  This suggests
that the critical shear rate scales linearly with the tension parameters.
Conversely, increasing (resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$
by up to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
relative \emph{decrease} (resp.~increasing) in the critical shear rate.  This points to an inverse-quadratic
scaling in length. Figure \ref{fig:PramChange}(a) summarizes the 
findings and suggest the scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under
shear flow.  Here $L$ is the diameter of the phase sample, which is
proportional to $\gamma^*$ since the striated phase tends to cleave
during rupture (see Supplementary Movie S4).  Our previous
work\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* = K_{\text{I}}
\gamma c^2/(\rho L^2)$ for vesicle BL in shear flow.

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). In
all cases, the vesicle and TG flow reach a steady-state tank-treading
motion, but the geometry and motion varies non-monotonically. For
$\lambda$ ranging from $1$ nm to $4$ nm, the steady-state vesicle shape
goes from an octagon, to a dimpled square, to a rounded diamond, to a
rounded square. Surprisingly, the direction of rotation switches: for
$\lambda = 2$ nm the rotation is clockwise, while for $\lambda = 4$ nm
the rotation is counterclockwise. Finally, we calculate the vesicle area
$A$ and length $L$. As shown in Figure~\ref{fig:PramChange}(f), the
relative area $A/A_0$ achieves a steady-state that is greatest for
$\lambda = 4$ nm yet least for $\lambda = 2$ nm. The relative length
$L/L_0$, however, is constant in $t$ for all cell sizes
(Figure~\ref{fig:PramChange}(e), inset). In other words, the flow
pattern is non-monotonic in the cell size $\lambda$.

We have excluded thermal fluctuations because they are unresolved in the
JP phases we consider.  For a tensionless, planar membrane, the spectrum
of the Fourier coefficients for the profile height 
$h(\xx) = \sum_{\kk} h(\kk)e^{i \kk \cdot \xx}$ satisfy\cite{Merath2006FluctuationSO}  
\begin{equation}
\label{eq:fourier_spectrum}
\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4},
\end{equation}
where $\xx$ is a point in an $L_x \times L_y$ rectangular membrane
patch, $\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with $m,n \in
\mathbb{Z}$, not both zero, and $\kappa$ is the membrane bending
modulus.

>>>>

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $2\pi \lambda \times 2\pi
\lambda$ TG cells. Throughout, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

In both cases, $\dot \gamma$ is the shear rate. The flow rate $\lambda
\dot \gamma$ is chosen so that~\eqref{eq:tg_flow} has the same rate of
viscous dissipation per area as for~\eqref{eq:sh_flow}. In other words,
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ is the
same for $\uu = \uu_{\infty}^{\text{sh}}$ as for $\uu =
\uu_{\infty}^{\text{TG}}$ when integrated over a TG cell $A$.

To obtain a range for $\dot \gamma$, consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$~nm and $\kappa = 20\;\kbt$ are the characteristic phase
sample radius and bending rigidity, respectively. That is, $\kappa$
gives the elastic stress for restoring the phase-sample shape. Shear
stress overcomes elastic stress when $C_a > 1$ and this yields $\dot
\gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s. Thus our values
for $\dot \gamma$ range between $0$ ns$^{-1}$ corresponding to quiescent
flow up to $0.2$~ns$^{-1}$ capable of rupturing the sample. Such shear
rates are compatible with molecular dynamics simulation
\cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA}, and shearing in blood capillary
vessels \cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.

For initial data, note that the steady-state Type I amphiphiles phase
consists of a number of disjoint bilayer components
(Figure~\ref{fig:relax}(b)). To also have a single-component Type I
phase, we reinitialize the data to have a ring-shaped vesicle bilayer.
This phase is distinguished from ``bilayer'' by ``vesicle BL'' in the
figures. For the same number of JP, the vesicle bilayer has lower free
steady-state energy ($F = 24.6 \;\kbt$ nm$^{-1}$) than the disordered
bilayer phase ($F = 27.2 \;\kbt$ nm$^{-1}$). Since the simulations are
for two dimensions, multiplying $F$ by a length gives the energy of a
transversely invariant, three-dimensional phase.

The simulation setup consists of placing each of the phases in either a
shear or TG background flow and then solving for the particle
trajectories in time. In each setup, we solved for $500$ time steps with
$\Delta t = 2$~ns, yielding time courses for $t \in [0, T]$, $T =
1$~$\upmu$s. We then post-process the trajectories.

Figure~\ref{fig:s2esummary}(e)--(l) show the typical streamlines for JP
phases in background flow. Although the plots only show the region near
the JP phases, the fluid velocity $\uu$ and order parameter $u$ are
accounted for in all of $\mathbb{R}^2$. Moreover, $\uu$ satisfies the
rigid boundary condition at every JP-fluid interface i.e., the particles
interact with the local flow field and are not merely carried by
background flow.

Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} contain the
fully-resolved time courses for the free energy $F$, alignment order
$S_2$, and strain $E$. The eight setups correspond to the four JP
phases---bilayer, vesicle BL, multilamellar, and striated---and two
background flows---shear and TG, and the data are plotted with the same
ordinate to facilitate comparisons between simulation setups. Each setup
considers a range of shear rates $\dot \gamma$ in the interval $[0,
0.2]$ ns$^{-1}$.

The fully-resolved time courses in Supplementary
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} contain significant
oscillations due to the particle-based formulation and tumbling inherent
to the background flows. To extract meaningful data, we further
post-process the $F$, $S_2$, $E$ curves by taking their time average
over the interval $t \in [0, T]$.

\subsection{Strain and alignment}
\label{sec:strain-alignment}
The plots reveal highly distinct material responses from each phase.
Figures~\ref{fig:s2esummary}(a) and (b) show the time-averaged strain
$\frac{1}{T}\int_0^T E \,\dif t$ over a broad range of shear rates.
Strain $E$ measures the non-rigid-body deformation relative to the
initial state and expectedly increases with shear rate. The greatest
increase occurs with the Type I amphiphiles, suggesting that this phase
has the lowest elastic modulus (squares). In comparison, the striated
phase consisting of Type III polar JP is basically rigid (triangles).

Figures~\ref{fig:s2esummary}(c) and (d) plot the time-averaged alignment
order $S_2$. The vesicle and striated phases possess the greatest
alignment order and, for the most part, $S_2$ decreases with increases
in shear rate. But there is an exception. The Type I bilayer phase
alignment order actually increases under both shear and TG flows (solid
squares). This suggests that the mixing action of background flow has
the effect of moving the disordered bilayer phase out of a local
equilibrium and into a state with greater order. This surprising
increase, brought about by combining previously broken bilayer end caps,
is accompanied by a slight decrease in free energy
(Figure~\ref{fig:fsummary}(a), solid squares).

The sudden jumps in Figures~\ref{fig:s2esummary}(a) and (b) and
commensurate drops in panels (c) and (d) indicate the existence of a
critical shear rate $\gamma_*$. This means that for $\gamma < \gamma_*$,
the JP phase remains intact while for $\gamma > \gamma_*$, the phase
ruptures. For example, the vesicle BL phase has $\gamma_*$ approximately
$0.05$ ns$^{-1}$ under shear flow and TG flow. However, the critical
shear rate is flow-pattern dependent because the striated phase has
$\gamma_* = 0.14$ ns$^{-1}$ under shear flow while $\gamma_* = 0.05$
ns$^{-1}$ under TG flow. Due to variable stress distribution, the
critical shear rate in TG flow likely depends on the cell size parameter
$\lambda$. The disordered bilayer phase does not really possess a
critical shear rate because it already consists of several, disjoint
components. The jump in Figure~\ref{fig:s2esummary}(a) (solid squares)
simply corresponds to disjoint components drifting apart in the shear
flow. The Type II multilamellar phase did not rupture for any of the
shear rates considered.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{FSummary.pdf}
\end{center}
\caption{\label{fig:fsummary}
  The change of average free energy versus shear rates for shear flow
  and TG flow simulation results are plotted in panels (a)-(b). Panel
  (c) contains quadratic fits to the change in free energy as a function
  of displacement in interparticle distance from equilibrium.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Free energy}
\label{sec:free-energy}
Figure~\ref{fig:fsummary} plots the time-averaged relative free energy
$\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$
is~\eqref{eq:free_energy2} at $t = 0$. The greatest increase occurs with
the Type II multilamellar phase, with the other phases showing a
moderate change in a few \KBT\,nm$^{-1}$.

Figure~\ref{fig:fsummary}(c) plots the free energy against the
displacement $x = c E$ representing the change in mean interparticle
displacement from equilibrium; $c = 1.25$~nm is the particle radius.
The energies in Figure~\ref{fig:fsummary}(c) are essentially quadratic
in $x$ suggesting that the interactions are harmonic locally around
equilibrium. The harmonic bond strength is strongest between polar JP,
and greater by a factor of two and five than that for asymmetric
hydrophobes and amphiphiles, respectively. This makes sense when
considering that the free energy of the steady-state striated phase is
also greatest (Figure~\ref{fig:relax}(c), around 85 \KBT\;nm$^{-1}$).
However, the bond strength in the multilamellar phase comes in second,
despite having least steady-state free energy (around
15~\KBT\;nm$^{-1}$). The data point to the fact that the binding
properties do not merely scale with free energy, but also involve the
details of the interface's hydrophobicity which are tuned
by~\eqref{eq:bc-type} in our model.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{RheologySummary.pdf}
\end{center}
\caption{\label{fig:rheologysummary} Rheology of Type I, II, and III
  phases. Panel (a) shows that bilayer phases behave as a Newtonian
  fluid. Panel (b) provides that the multilamellar phase shows a near
  shear thinning behaviour. A pseudoplastic behaviour of deformation in
  striated phases is shown in panel (c).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely constant
strains maintained by an external force provided by background flow.
Now we consider dynamic material properties. Specifically, we look at
the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that the shear flow
$\uu_{\infty}^{\text{sh}}$ simulations correspond to a complex fluid
within a drag plate rheometer where the shear stress is set by $\mu
\dot\gamma$ and the observed, sample shear rate is $\dot E$. The
definitions carry over to the TG flow case directly. Also, as a
practical consideration, the rotation of non-isotropic JP phases in the
background flow leads to oscillation in the strain time courses making
systematic fitting challenging (see Supplementary Material
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}). The integral
in~\eqref{eq:strainrate} averages out these oscillations and gives
physically meaningful values.

The shear stress-strain rate data are excellently fit by power laws.
Figures~\ref{fig:rheologysummary}(a)--(c) show the data for Type I, Type
II and Type III JPs, respectively, under both shear flow (squares) and
TG flow (triangles). The bilayer phases consisting of Type I JPs are
basically Newtonian with viscosity $0.014$ MPa\;$\upmu$s $= 14$ mPa\;s,
about 14 times the viscosity of water at room temperature
(Figures~\ref{fig:rheologysummary}(a), dashed curve). The vesicle
bilayer phase is slightly shear thickening
(Figure~\ref{fig:rheologysummary}(a), solid curve). The multilamellar
phase consisting of Type II JPs is somewhat shear thinning, but its
viscosity is larger than for Type I. Finally, the striated phase is
strongly shear-thinning. This further explains the rigid-like behavior
of the striated phase found in the strain, shear-rate relationships from
Figures~\ref{fig:s2esummary}(a) and (b) (triangles).
\todo[inline]{RBC flow refereces}

@@

\subsection{Discussion}
We choose the range of shear rates $\dot \gamma \in [0, 0.02]$~ns$^{-1}$
by analyzing the capillary number of the JP phases. With this range,
there is a critical shear rate $\dot \gamma_*$ for the vesicle BL and
striated phases where shear stresses exceeded elastic stresses, leading
to rupture. The multilamellar phase did not rupture. By varying model
parameters, we perform a dimensional analysis on $\dot \gamma_*$.
Focusing on Type III JPs in shear flow, $\dot \gamma_* = 0.14$ ns$^{-1}$
for the basic model parameters (see
Section~\ref{sec:tunable_hydrophobicity}). Increasing and decreasing the
tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
$\Delta \gamma/\gamma$) led to basically the same relative
increase/decrease in critical shear rate (denoted $\Delta \dot
\gamma_*/\dot \gamma_*$). This suggests that the critical shear rate
scales linearly with the tension parameters. Conversely, increasing
(resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$ by up
to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
relative \emph{decrease} (resp.~increase) in the critical shear rate.
This points to an inverse-quadratic scaling in length.
Figure~\ref{fig:PramChange}(a) summarizes the findings and suggest the
scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under
shear flow. Here $L$ is the diameter of the phase sample, which is
proportional to $\gamma^*$ since the striated phase tends to cleave
during rupture (see Supplementary Movie S4). Our previous
work~\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* =
K_{\text{I}} \gamma c^2/(\rho L^2)$ for a vesicle BL in shear flow.

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). In
all cases, the vesicle and TG flow reach a steady-state tank-treading
motion \todo[inline]{no longer true}, but the geometry and motion varies
non-monotonically. For $\lambda$ ranging from $1$ nm to $4$ nm, the
steady-state vesicle shape goes from an octagon, to a dimpled square, to
a rounded diamond, to a rounded square. Surprisingly, the direction of
rotation switches: for $\lambda = 2$ nm the rotation is clockwise, while
for $\lambda = 4$ nm the rotation is counterclockwise. Finally, we
calculate the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area $A/A_0$ achieves a
steady-state that is greatest for $\lambda = 4$ nm yet least for
$\lambda = 2$ nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (Figure~\ref{fig:PramChange}(e), inset). In other
words, the flow pattern is non-monotonic in the cell size $\lambda$.

We have excluded thermal fluctuations because they are unresolved in the
JP phases we consider. For a tensionless, planar membrane, the Fourier
coefficients for the profile height $h(\xx) = \sum_{\kk} h(\kk)e^{i \kk
\cdot \xx}$ satisfy~\cite{Merath2006FluctuationSO}  
\begin{equation}
\label{eq:fourier_spectrum}
\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4},
\end{equation}
where $\xx$ is a point in an $L_x \times L_y$ rectangular membrane
patch, $\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with $m,n \in
\mathbb{Z}$, not both zero, and $\kappa$ is the membrane bending
modulus.
